---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
  <!-- badges: start -->
  [![R-CMD-check](https://github.com/cfjdoedens/binompoiscont/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/cfjdoedens/binompoiscont/actions/workflows/R-CMD-check.yaml)
  [![Codecov test coverage](https://codecov.io/gh/cfjdoedens/binompoiscont/graph/badge.svg)](https://app.codecov.io/gh/cfjdoedens/binompoiscont)
[![Deploy Shiny App](https://github.com/cfjdoedens/binompoiscont/actions/workflows/deploy-shiny.yaml/badge.svg)](https://github.com/cfjdoedens/binompoiscont/actions/workflows/deploy-shiny.yaml)  
  <!-- badges: end -->

```{r setup, include=FALSE}
# README.Rmd is processed by the developer of the package 
# to create a README.md or README.html for the user of the package.
# The README should be processed as last step in the development process.
# This means that we should load here the latest version of the package.
# So that is what we will do below.
# 
# Also when we are developing the package and 
# in parallel writing the README, we want to use for the
# README the latest version of the package.
# 
# Load the latest version of the package that is under development.
if (requireNamespace("devtools", quietly = TRUE) && 
    file.exists("binompoiscont.Rproj")) {
  devtools::load_all(".")
} else {
  # Error! Break off knitting process.
  stop("README binompoiscont: no binompoiscont.Rproj in current directory.")
}

# Set global knitr options for all subsequent chunks
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  
  # Route messages, warnings and errors to the R console, i.e. the developer.
  # Not to the resulting document, i.e. the reader.
  message = FALSE, 
  warning = FALSE, 
  error = FALSE
)
```

# binompoiscont

The goal of binompoiscont is to provide continuous versions of the binomial and 
Poisson distributions. These versions are implemented as the functions
`dbinom_continuous(k, n, p)`, `dpois3_continuous(k, n, p)`
and `dpois_continuous(x, lambda)`.

For a background article see 
"Continuous counterparts of Poisson and binomial distributions and their properties"
by Andrii Ilienko.
For example to be found through the following link: https://arxiv.org/abs/1303.5990.

The function `dbinom_continuous()` provided by this package is based on a
beta() function equivalent.
This is done by straightforward derivation of both shape parameters, `shape1`, and `shape2`,
from the arguments `k` and `n` for `dbinom()`. `shape1 = k + 1`, `shape2 = n - k + 1`.
It is not clear to me how to derive
the beta function shape parameters `shape1` and `shape2` from the parameters of
`pbinom()`, `qbinom()`, `rbinom()`.
The parameter `k`, or an equivalent, is not used by these functions.
And I do not know how to formulate in other ways equivalent
(but continuous) beta functions for `pbinom()`, `qbinom()`, and `rbinom()`
functions. Therefore continuous versions
of these latter functions are not provided in this package.

The functions `dpois_continous()` and `dpois3_continous()` are based
on the `gamma()` function. I have not looked into how to find continuous
versions for `ppois()`, `qpois()` and `rpois()`. 

## Installation

You can install the development version of binompoiscont from
[GitHub](https://github.com/) with:

```{r install, eval = FALSE, echo=TRUE}
  if (!requireNamespace("devtools", quietly = TRUE)) {
    install.packages("devtools")
  }
  devtools::install_github("cfjdoedens/binompoiscont")
```

## Interactive Visualization

Want to see the distributions in action? This package includes a Shiny app.
Run this in your R console:

binompoiscont::run_app()

## Example

The following code shows the usefulness of dbinom_continuous(k, n, p), 
dpois3_continuous(k, n, p) and dpois_continuous(x, lambda).


```{r example}
library(binompoiscont)
## Suppose we do 10.3 trials with a probability of success of 0.3, and we
## want to know the probability that the sum of the successes
## is 3.5.
n <- 10.3
k <- 3.5
p <- 0.3

## If we use the dbinom() function we get an error: computer says no, can't do this.
dbinom(k, n, p)

## The same for the dpois() function.
dpois(k, n * p)

## But this probability can be calculated with the continuous versions.
dbinom_continuous(k, n, p)
dpois3_continuous(k, n, p)
dpois_continuous(k, n * p)
```

