---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# binompoiscont

<!-- badges: start -->
<!-- badges: end -->

The goal of binompoiscont is to provide continuous versions of the binomial and 
Poisson distributions. These versions are implemented as the functions
dbinom_continuous(k, n, p), dpois3_continuous(k, n, p)
and dpois_continuous(x, lambda).

For a background article see 
"Continuous counterparts of Poisson and binomial distributions and their properties"
by Andrii Ilienko.
For example to be found through the following link: https://arxiv.org/abs/1303.5990.

## Installation

You can install the development version of binompoiscont from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("cfjdoedens/binompoiscont")
```

## Example

The following code shows the usefulness of dbinom_continuous(k, n, p), 
dpois3_continuous(k, n, p) and dpois_continuous(x, lambda).


```{r example}
library(binompoiscont)
## Suppose we do 10.3 trials with a probability of success of 0.3, and we
## want to know the probability that the sum of the successes
## is 3.5.
n <- 10.3
k <- 3.5
p <- 0.3

## If we use the dbinom() function we get an error: computer says no, can't do this.
dbinom(k, n, p)

## The same for the dpois() function.
dpois(k, n * p)

## But his probability can be calculated with the continuous versions.
dbinom_continuous(k, n, p)
dpois3_continuous(k, n, p)
dpois_continuous(k, n * p)
```

